EDIpack: A generic and interoperable Lanczos-based solver for quantum impurity problems

### 2025-05-23 04_cbinding.tex

\subsubsection{Installation}\label{sSecInteropEDIpyInstallation}
\paragraph{From source}
EDIpack2py is available as a Python
module which only depends on \NAME and SciFortran.
The Python package can be obtained from the repository
\href{https://github.com/EDIpack/EDIpack2py}{EDIpack2py}.

@@

\paragraph{Anaconda}
As for \NAME, the Python API in EDIpack2py is available through
Anaconda packaging for Unix/Linux systems. Packages are available for
Python version $>3.10$. The \NAME package contains the {\tt
  EDIpack2py} Python module as well as \NAME and SciFortran
libraries. In this case the resolution of the dependencies is
taken care from Conda itself. 
Using conda the installation reads:
\begin{lstlisting}[style=mybash]
conda create -n edipack
conda activate edipack
conda install -c conda-forge -c edipack edipack
\end{lstlisting}

>>>>

\subsubsection{Installation}\label{sSecInteropEDIpyInstallation}
\paragraph{From source}
EDIpack2py is available as a platform-agnostic Python module depending on EDIpack.
The source code can be obtained from the git repository \href{https://github.com/EDIpack/EDIpack2py}{EDIpack2py} and installed via

@@

\paragraph{Anaconda}
As for \NAME, the Python API in EDIpack2py is available as an
Anaconda package for GNU/Linux and Mac Os systems. Packages are available for
Python version $>3.10$. The \NAME package contains the {\tt
  EDIpack2py} Python module as well as \NAME and SciFortran
libraries. In this case the resolution of the dependencies is
taken care from Conda itself. 
Using conda the installation reads:
\begin{lstlisting}[style=mybash]
conda create -n edipack
conda activate edipack
conda install -c conda-forge -c edipack edipack
\end{lstlisting}
